NTM CT Scoring - Initial Agreement

### 2023-05-18 Stacey Martiniano/ntm_agreement.qmd
tidyverse formatting

```{r}
#| include: false
library(tidyverse)
library(irr)
library(redcapAPI)
library(Hmisc)
library(DT)
library(RColorBrewer)
library(knitr)
library(pheatmap)
# Import data
api <- read.table("~/Documents/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/api.txt",
                  header = F
)
rcon <- redcapConnection(
  url = "https://redcap.ucdenver.edu/api/",
  token = api[1, 1]
)
data <- exportRecords(rcon, labels = F)
data <- data.frame(lapply(data, as.character))
data$scan_id = as.numeric(data$scan_id)
# Make scorer IDs by initial
data$scorer <- paste0(
  toupper(substr(data$reader_first_name, 1, 1)),
  toupper(substr(data$reader_last_name, 1, 1))
)
data$scorer[data$scorer=="GG"]="GS"
# Deidentify readers
old <- c("AF","DL","JW")
new <- c("A","B","C")
data$scorer[data$scorer %in% old] <- new[match(data$scorer, old, nomatch = 0)]
# Revert duplicate IDs back to original to match with gold standard
training = read.csv("~/Documents/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/Data_Clean/training.key.csv")
dups = read.csv("~/Documents/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/Data_Clean/duplicated.key.csv")
training$Training_id = as.numeric(sub("T00","",training$Training_id))
# Change duplicates to OG IDs
old <- dups$duplicated_ssid..dates.shifted..17.days.
new <- dups$original_ssid
data$scan_id[data$scan_id %in% old] <- new[match(data$scan_id, old, nomatch = 0)]
# Change training IDs to OG IDs
old <- training$Training_id
new = training$Cffid.Scoring.Set
data$scan_id[data$scan_id %in% old] <- new[match(data$scan_id, old, nomatch = 0)]
# Plot colors
name <- "Accent"
colors <- brewer.pal(6, name)
names(colors) <- c("Checked","Unchecked","Absent","Cylindric","Varicose",NA)
custom_colors <- scale_fill_manual(name = "", values = colors)
```

@@

```{r}
# Gold standard data
gs = data %>% 
  arrange(scan_id, scorer) %>%
  filter(scan_id %in% training$Cffid.Scoring.Set) %>%
  group_by(scorer,scan_id) %>%
  slice_max(scoresheet_timestamp) %>%
  select(scorer, scan_id, bronchiectasis_rul:atelectasis___6) %>%
  ungroup() %>% pivot_longer(bronchiectasis_rul:atelectasis___6,
                             names_to = c("feature", "location"),
                             names_pattern = "(.*)_(.*)$"
  ) %>% 
  mutate(
    feature = gsub("__", "", feature),
    feature = str_to_title(gsub("_", " ", feature))
  ) 
gs$location <- factor(gs$location,
                      levels = c("1", "2", "3", "4", "5", "6", "ling", "lll", 
                                 "lul", "rll", "rml", "rul"),
                      labels = c("RUL", "RML", "RLL", "LUL", "Ling", "LLL", 
                                 "Ling", "LLL", "LUL", "RLL", "RML", "RUL")
)
# One column per scorer
gs <- gs %>% 
  pivot_wider(names_from = scorer, values_from = value) %>%
  arrange(feature,location)
```

@@

```{r}
gs_bronch = gs %>% filter(feature=="Bronchiectasis")
fk = kappam.fleiss(gs_bronch[,c("A","B","C","GS")])
A = kappa2(gs_bronch[,c("A","GS")])
B = kappa2(gs_bronch[,c("B","GS")])
C = kappa2(gs_bronch[,c("C","GS")])
# Plot
gs_bronch %>%
  select(scan_id,feature, location, A:GS) %>%
  pivot_longer(A:GS) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

@@

```{r}
gs_other = gs %>% filter(feature!="Bronchiectasis")
# Check agreement with GS column
gs_other$A = factor(gs_other$A == gs_other$GS,levels = c(F,T),labels = c("Disagree","Agree"))
gs_other$B = factor(gs_other$B == gs_other$GS,levels = c(F,T),labels = c("Disagree","Agree"))
gs_other$C = factor(gs_other$C == gs_other$GS,levels = c(F,T),labels = c("Disagree","Agree"))
# Plot
gs_other %>%
  select(scan_id,feature, location, A:GS) %>%
  pivot_longer(A:C) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  facet_grid(rows = vars(feature),cols = vars(scan_id))
# Tables
gs_other %>%
  summarise(across(A:C,~mean(.x == "Agree",na.rm = T)),.groups = "drop") %>%
  kable(.,digits=3,caption = "Proportion of agreement with GS")
gs_other %>%
  group_by(scan_id) %>%
  summarise(across(A:C,~mean(.x == "Agree",na.rm = T)),.groups = "drop") %>%
  kable(.,digits=3,caption = "Proportion of agreement with GS")
gs_other %>%
  group_by(feature) %>%
  summarise(across(A:C,~mean(.x == "Agree",na.rm = T)),.groups = "drop") %>%
  kable(.,digits=3,caption = "Proportion of agreement with GS")
gs_other %>%
  group_by(scan_id,feature) %>%
  summarise(across(A:C,~mean(.x == "Agree",na.rm = T)),.groups = "drop") %>%
  kable(.,digits=3,caption = "Proportion of agreement with GS")
# Heatmaps
gs_other %>%
  group_by(scan_id) %>%
  summarise(across(A:C,~mean(.x == "Agree",na.rm = T)),.groups = "keep") %>%
  column_to_rownames("scan_id") %>%
  pheatmap(.,cluster_rows = F,cluster_cols = F)
gs_other %>%
  group_by(feature) %>%
  summarise(across(A:C,~mean(.x == "Agree",na.rm = T)),.groups = "keep") %>%
  column_to_rownames("feature") %>%
  pheatmap(.,cluster_rows = F,cluster_cols = F)
gs_other %>%
  group_by(scan_id,feature) %>%
  summarise(across(A:C,~mean(.x == "Agree",na.rm = T)),.groups = "keep") %>%
  unite(ids,scan_id,feature,na.rm = T,sep = " ") %>%
  column_to_rownames("ids") %>%
  pheatmap(.,cluster_rows = F,cluster_cols = F)
```

@@

```{r}
# Gold standard data
dup = data %>% 
  arrange(scan_id, scorer) %>%
  filter(scan_id %in% dups$original_ssid) %>%
  group_by(scorer,scan_id) %>%
  mutate(n=row_number())%>%
  select(scorer, scan_id,n ,bronchiectasis_rul:atelectasis___6) %>%
  ungroup() %>% pivot_longer(bronchiectasis_rul:atelectasis___6,
                             names_to = c("feature", "location"),
                             names_pattern = "(.*)_(.*)$"
  ) %>% 
  mutate(
    feature = gsub("__", "", feature),
    feature = str_to_title(gsub("_", " ", feature))
  ) 
dup$location <- factor(dup$location,
                       levels = c("1", "2", "3", "4", "5", "6", "ling", "lll", 
                                  "lul", "rll", "rml", "rul"),
                       labels = c("RUL", "RML", "RLL", "LUL", "Ling", "LLL", 
                                  "Ling", "LLL", "LUL", "RLL", "RML", "RUL")
)
# One column per scorer
dup <- dup %>% 
  pivot_wider(names_from = scorer, values_from = value) %>%
  pivot_wider(names_from = n, values_from = A:C) %>%
  arrange(feature,location)
```

@@

```{r}
dup_bronch = dup %>% filter(feature=="Bronchiectasis")
A = kappa2(dup_bronch[,c("A_1","A_2")])
B = kappa2(dup_bronch[,c("B_1","B_2")])
C = kappa2(dup_bronch[,c("C_1","C_2")])
# Plot
dup_bronch %>%
  select(scan_id,feature, location,A_1:C_2) %>%
  pivot_longer(A_1:C_2) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Cohen's Kappa for A vs. themselves was `r round(A$value,3)` (p = `r format.pval(A$p.value,eps = 0.001,digits = 3)`).

Cohen's Kappa for B vs. themselves was `r round(B$value,3)` (p = `r format.pval(B$p.value,eps = 0.001,digits = 3)`).

Cohen's Kappa for C vs. themselves was `r round(C$value,3)` (p = `r format.pval(C$p.value,eps = 0.001,digits = 3)`).

@@

```{r}
dup_other = dup %>% filter(feature!="Bronchiectasis")
# Check agreement with GS column
dup_other$A = factor(dup_other$A_1 == dup_other$A_2,levels = c(F,T),labels = c("Disagree","Agree"))
dup_other$B = factor(dup_other$B_1 == dup_other$B_2,levels = c(F,T),labels = c("Disagree","Agree"))
dup_other$C = factor(dup_other$C_1 == dup_other$C_2,levels = c(F,T),labels = c("Disagree","Agree"))
# Plot
dup_other %>%
  select(scan_id,feature, location, A:C) %>%
  pivot_longer(A:C) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  facet_grid(rows = vars(feature),cols = vars(scan_id))
# Tables
dup_other %>%
  summarise(across(A:C,~mean(.x == "Agree",na.rm = T)),.groups = "drop") %>%
  kable(.,digits=3,caption = "Proportion of agreement with themselves")
dup_other %>%
  group_by(scan_id) %>%
  summarise(across(A:C,~mean(.x == "Agree",na.rm = T)),.groups = "drop") %>%
  kable(.,digits=3,caption = "Proportion of agreement with themselves")
dup_other %>%
  group_by(feature) %>%
  summarise(across(A:C,~mean(.x == "Agree",na.rm = T)),.groups = "drop") %>%
  kable(.,digits=3,caption = "Proportion of agreement with themselves")
dup_other %>%
  group_by(scan_id,feature) %>%
  summarise(across(A:C,~mean(.x == "Agree",na.rm = T)),.groups = "drop") %>%
  kable(.,digits=3,caption = "Proportion of agreement with themselves")
# Heatmaps
dup_other %>%
  group_by(scan_id) %>%
  summarise(across(A:C,~mean(.x == "Agree",na.rm = T)),.groups = "keep") %>%
  column_to_rownames("scan_id") %>%
  pheatmap(.,cluster_rows = F,cluster_cols = F)
dup_other %>%
  group_by(feature) %>%
  summarise(across(A:C,~mean(.x == "Agree",na.rm = T)),.groups = "keep") %>%
  column_to_rownames("feature") %>%
  pheatmap(.,cluster_rows = F,cluster_cols = F)
dup_other %>%
  group_by(scan_id,feature) %>%
  summarise(across(A:C,~mean(.x == "Agree",na.rm = T)),.groups = "keep") %>%
  unite(ids,scan_id,feature,na.rm = T,sep = " ") %>%
  column_to_rownames("ids") %>%
  pheatmap(.,cluster_rows = F,cluster_cols = F)
```

>>>>

```{r}
#| include: false
library(tidyverse)
library(irr)
library(redcapAPI)
library(Hmisc)
library(DT)
library(RColorBrewer)
library(knitr)
library(pheatmap)
# Import data
api <- read.table("~/Documents/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/api.txt",
  header = F
)
rcon <- redcapConnection(
  url = "https://redcap.ucdenver.edu/api/",
  token = api[1, 1]
)
data <- exportRecords(rcon, labels = F)
data <- data.frame(lapply(data, as.character))
data$scan_id <- as.numeric(data$scan_id)
# Make scorer IDs by initial
data$scorer <- paste0(
  toupper(substr(data$reader_first_name, 1, 1)),
  toupper(substr(data$reader_last_name, 1, 1))
)
data$scorer[data$scorer == "GG"] <- "GS"
# Deidentify readers
old <- c("AF", "DL", "JW")
new <- c("A", "B", "C")
data$scorer[data$scorer %in% old] <- new[match(data$scorer, old, nomatch = 0)]
# Revert duplicate IDs back to original to match with gold standard
training <- read.csv("~/Documents/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/Data_Clean/training.key.csv")
dups <- read.csv("~/Documents/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/Data_Clean/duplicated.key.csv")
training$Training_id <- as.numeric(sub("T00", "", training$Training_id))
# Change duplicates to OG IDs
old <- dups$duplicated_ssid..dates.shifted..17.days.
new <- dups$original_ssid
data$scan_id[data$scan_id %in% old] <- new[match(data$scan_id, old, nomatch = 0)]
# Change training IDs to OG IDs
old <- training$Training_id
new <- training$Cffid.Scoring.Set
data$scan_id[data$scan_id %in% old] <- new[match(data$scan_id, old, nomatch = 0)]
# Plot colors
name <- "Accent"
colors <- brewer.pal(6, name)
names(colors) <- c("Checked", "Unchecked", "Absent", "Cylindric", "Varicose", NA)
custom_colors <- scale_fill_manual(name = "", values = colors)
```

@@

```{r}
# Gold standard data
gs <- data %>%
  arrange(scan_id, scorer) %>%
  filter(scan_id %in% training$Cffid.Scoring.Set) %>%
  group_by(scorer, scan_id) %>%
  slice_max(scoresheet_timestamp) %>%
  select(scorer, scan_id, bronchiectasis_rul:atelectasis___6) %>%
  ungroup() %>%
  pivot_longer(bronchiectasis_rul:atelectasis___6,
    names_to = c("feature", "location"),
    names_pattern = "(.*)_(.*)$"
  ) %>%
  mutate(
    feature = gsub("__", "", feature),
    feature = str_to_title(gsub("_", " ", feature))
  )
gs$location <- factor(gs$location,
  levels = c(
    "1", "2", "3", "4", "5", "6", "ling", "lll",
    "lul", "rll", "rml", "rul"
  ),
  labels = c(
    "RUL", "RML", "RLL", "LUL", "Ling", "LLL",
    "Ling", "LLL", "LUL", "RLL", "RML", "RUL"
  )
)
# One column per scorer
gs <- gs %>%
  pivot_wider(names_from = scorer, values_from = value) %>%
  arrange(feature, location)
```

@@

```{r}
gs_bronch <- gs %>% filter(feature == "Bronchiectasis")
fk <- kappam.fleiss(gs_bronch[, c("A", "B", "C", "GS")])
A <- kappa2(gs_bronch[, c("A", "GS")])
B <- kappa2(gs_bronch[, c("B", "GS")])
C <- kappa2(gs_bronch[, c("C", "GS")])
# Plot
gs_bronch %>%
  select(scan_id, feature, location, A:GS) %>%
  pivot_longer(A:GS) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

@@

```{r}
gs_other <- gs %>% filter(feature != "Bronchiectasis")
# Check agreement with GS column
gs_other$A <- factor(gs_other$A == gs_other$GS, levels = c(F, T), labels = c("Disagree", "Agree"))
gs_other$B <- factor(gs_other$B == gs_other$GS, levels = c(F, T), labels = c("Disagree", "Agree"))
gs_other$C <- factor(gs_other$C == gs_other$GS, levels = c(F, T), labels = c("Disagree", "Agree"))
# Plot
gs_other %>%
  select(scan_id, feature, location, A:GS) %>%
  pivot_longer(A:C) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  facet_grid(rows = vars(feature), cols = vars(scan_id))
# Tables
gs_other %>%
  summarise(across(A:C, ~ mean(.x == "Agree", na.rm = T)), .groups = "drop") %>%
  kable(., digits = 3, caption = "Proportion of agreement with GS")
gs_other %>%
  group_by(scan_id) %>%
  summarise(across(A:C, ~ mean(.x == "Agree", na.rm = T)), .groups = "drop") %>%
  kable(., digits = 3, caption = "Proportion of agreement with GS")
gs_other %>%
  group_by(feature) %>%
  summarise(across(A:C, ~ mean(.x == "Agree", na.rm = T)), .groups = "drop") %>%
  kable(., digits = 3, caption = "Proportion of agreement with GS")
gs_other %>%
  group_by(scan_id, feature) %>%
  summarise(across(A:C, ~ mean(.x == "Agree", na.rm = T)), .groups = "drop") %>%
  kable(., digits = 3, caption = "Proportion of agreement with GS")
# Heatmaps
gs_other %>%
  group_by(scan_id) %>%
  summarise(across(A:C, ~ mean(.x == "Agree", na.rm = T)), .groups = "keep") %>%
  column_to_rownames("scan_id") %>%
  pheatmap(., cluster_rows = F, cluster_cols = F)
gs_other %>%
  group_by(feature) %>%
  summarise(across(A:C, ~ mean(.x == "Agree", na.rm = T)), .groups = "keep") %>%
  column_to_rownames("feature") %>%
  pheatmap(., cluster_rows = F, cluster_cols = F)
gs_other %>%
  group_by(scan_id, feature) %>%
  summarise(across(A:C, ~ mean(.x == "Agree", na.rm = T)), .groups = "keep") %>%
  unite(ids, scan_id, feature, na.rm = T, sep = " ") %>%
  column_to_rownames("ids") %>%
  pheatmap(., cluster_rows = F, cluster_cols = F)
```

@@

```{r}
# Gold standard data
dup <- data %>%
  arrange(scan_id, scorer) %>%
  filter(scan_id %in% dups$original_ssid) %>%
  group_by(scorer, scan_id) %>%
  mutate(n = row_number()) %>%
  select(scorer, scan_id, n, bronchiectasis_rul:atelectasis___6) %>%
  ungroup() %>%
  pivot_longer(bronchiectasis_rul:atelectasis___6,
    names_to = c("feature", "location"),
    names_pattern = "(.*)_(.*)$"
  ) %>%
  mutate(
    feature = gsub("__", "", feature),
    feature = str_to_title(gsub("_", " ", feature))
  )
dup$location <- factor(dup$location,
  levels = c(
    "1", "2", "3", "4", "5", "6", "ling", "lll",
    "lul", "rll", "rml", "rul"
  ),
  labels = c(
    "RUL", "RML", "RLL", "LUL", "Ling", "LLL",
    "Ling", "LLL", "LUL", "RLL", "RML", "RUL"
  )
)
# One column per scorer
dup <- dup %>%
  pivot_wider(names_from = scorer, values_from = value) %>%
  pivot_wider(names_from = n, values_from = A:C) %>%
  arrange(feature, location)
```

@@

```{r}
dup_bronch <- dup %>% filter(feature == "Bronchiectasis")
A <- kappa2(dup_bronch[, c("A_1", "A_2")])
B <- kappa2(dup_bronch[, c("B_1", "B_2")])
C <- kappa2(dup_bronch[, c("C_1", "C_2")])
# Plot
dup_bronch %>%
  select(scan_id, feature, location, A_1:C_2) %>%
  pivot_longer(A_1:C_2) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Overall Cohen's Kappa for A vs. themselves was `r round(A$value,3)` (p = `r format.pval(A$p.value,eps = 0.001,digits = 3)`).

Overall Cohen's Kappa for B vs. themselves was `r round(B$value,3)` (p = `r format.pval(B$p.value,eps = 0.001,digits = 3)`).

Overall Cohen's Kappa for C vs. themselves was `r round(C$value,3)` (p = `r format.pval(C$p.value,eps = 0.001,digits = 3)`).

@@

```{r}
dup_other <- dup %>% filter(feature != "Bronchiectasis")
# Check agreement with GS column
dup_other$A <- factor(dup_other$A_1 == dup_other$A_2, levels = c(F, T), labels = c("Disagree", "Agree"))
dup_other$B <- factor(dup_other$B_1 == dup_other$B_2, levels = c(F, T), labels = c("Disagree", "Agree"))
dup_other$C <- factor(dup_other$C_1 == dup_other$C_2, levels = c(F, T), labels = c("Disagree", "Agree"))
# Plot
dup_other %>%
  select(scan_id, feature, location, A:C) %>%
  pivot_longer(A:C) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  facet_grid(rows = vars(feature), cols = vars(scan_id))
# Tables
dup_other %>%
  summarise(across(A:C, ~ mean(.x == "Agree", na.rm = T)), .groups = "drop") %>%
  kable(., digits = 3, caption = "Proportion of agreement with themselves")
dup_other %>%
  group_by(scan_id) %>%
  summarise(across(A:C, ~ mean(.x == "Agree", na.rm = T)), .groups = "drop") %>%
  kable(., digits = 3, caption = "Proportion of agreement with themselves")
dup_other %>%
  group_by(feature) %>%
  summarise(across(A:C, ~ mean(.x == "Agree", na.rm = T)), .groups = "drop") %>%
  kable(., digits = 3, caption = "Proportion of agreement with themselves")
dup_other %>%
  group_by(scan_id, feature) %>%
  summarise(across(A:C, ~ mean(.x == "Agree", na.rm = T)), .groups = "drop") %>%
  kable(., digits = 3, caption = "Proportion of agreement with themselves")
# Heatmaps
dup_other %>%
  group_by(scan_id) %>%
  summarise(across(A:C, ~ mean(.x == "Agree", na.rm = T)), .groups = "keep") %>%
  column_to_rownames("scan_id") %>%
  pheatmap(., cluster_rows = F, cluster_cols = F)
dup_other %>%
  group_by(feature) %>%
  summarise(across(A:C, ~ mean(.x == "Agree", na.rm = T)), .groups = "keep") %>%
  column_to_rownames("feature") %>%
  pheatmap(., cluster_rows = F, cluster_cols = F)
dup_other %>%
  group_by(scan_id, feature) %>%
  summarise(across(A:C, ~ mean(.x == "Agree", na.rm = T)), .groups = "keep") %>%
  unite(ids, scan_id, feature, na.rm = T, sep = " ") %>%
  column_to_rownames("ids") %>%
  pheatmap(., cluster_rows = F, cluster_cols = F)
```

# Singleton scans

```{r}
# Gold standard data
df <- data %>%
  arrange(scan_id, scorer) %>%
  filter(!(scan_id %in% dups$original_ssid) &
    !(scan_id %in% training$Cffid.Scoring.Set)) %>%
  select(scorer, scan_id, bronchiectasis_rul:atelectasis___6) %>%
  pivot_longer(bronchiectasis_rul:atelectasis___6,
    names_to = c("feature", "location"),
    names_pattern = "(.*)_(.*)$"
  ) %>%
  mutate(
    feature = gsub("__", "", feature),
    feature = str_to_title(gsub("_", " ", feature))
  )
df$location <- factor(df$location,
  levels = c(
    "1", "2", "3", "4", "5", "6", "ling", "lll",
    "lul", "rll", "rml", "rul"
  ),
  labels = c(
    "RUL", "RML", "RLL", "LUL", "Ling", "LLL",
    "Ling", "LLL", "LUL", "RLL", "RML", "RUL"
  )
)
# One column per scorer
df <- df %>%
  pivot_wider(names_from = scorer, values_from = value) %>%
  arrange(feature, location)
```

```{r}
df_bronch <- df %>% filter(feature == "Bronchiectasis")
fk <- kappam.fleiss(df_bronch[, c("A", "B", "C")])
# Plot
df_bronch %>%
  select(scan_id, feature, location, A:C) %>%
  pivot_longer(A:C) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Overall Fleiss' Kappa for all 15 singleton scans was `r round(fk$value,3)` (p = `r format.pval(fk$p.value,eps = 0.001,digits = 3)`).

```{r}
df_other <- df %>% filter(feature != "Bronchiectasis")
# Check agreement with GS column
df_other[, c("A", "B", "C")] <- lapply(df_other[, c("A", "B", "C")], factor,
  levels = c("Unchecked", "Checked"),
  labels = c("Absent", "Present")
)
# Three-way agreement
df_other$`A vs. B` <- factor(df_other$A == df_other$B, levels = c(F, T), labels = c("Disagree", "Agree"))
df_other$`A vs. C` <- factor(df_other$A == df_other$C, levels = c(F, T), labels = c("Disagree", "Agree"))
df_other$`B vs. C` <- factor(df_other$B == df_other$C, levels = c(F, T), labels = c("Disagree", "Agree"))
# Plot
df_other %>%
  select(scan_id, feature, location, `A vs. B`:`B vs. C`) %>%
  pivot_longer(`A vs. B`:`B vs. C`) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  facet_grid(rows = vars(feature), cols = vars(scan_id))
# Tables
df_other %>%
  summarise(across(`A vs. B`:`B vs. C`, ~ mean(.x == "Agree", na.rm = T)), .groups = "drop") %>%
  kable(., digits = 3, caption = "Proportion of agreement with themselves")
df_other %>%
  group_by(scan_id) %>%
  summarise(across(`A vs. B`:`B vs. C`, ~ mean(.x == "Agree", na.rm = T)), .groups = "drop") %>%
  kable(., digits = 3, caption = "Proportion of agreement with themselves")
df_other %>%
  group_by(feature) %>%
  summarise(across(`A vs. B`:`B vs. C`, ~ mean(.x == "Agree", na.rm = T)), .groups = "drop") %>%
  kable(., digits = 3, caption = "Proportion of agreement with themselves")
df_other %>%
  group_by(scan_id, feature) %>%
  summarise(across(`A vs. B`:`B vs. C`, ~ mean(.x == "Agree", na.rm = T)), .groups = "drop") %>%
  kable(., digits = 3, caption = "Proportion of agreement with themselves")
# Heatmaps
df_other %>%
  group_by(scan_id) %>%
  summarise(across(`A vs. B`:`B vs. C`, ~ mean(.x == "Agree", na.rm = T)), .groups = "keep") %>%
  column_to_rownames("scan_id") %>%
  pheatmap(., cluster_rows = F, cluster_cols = F)
df_other %>%
  group_by(feature) %>%
  summarise(across(`A vs. B`:`B vs. C`, ~ mean(.x == "Agree", na.rm = T)), .groups = "keep") %>%
  column_to_rownames("feature") %>%
  pheatmap(., cluster_rows = F, cluster_cols = F)
df_other %>%
  group_by(scan_id, feature) %>%
  summarise(across(`A vs. B`:`B vs. C`, ~ mean(.x == "Agree", na.rm = T)), .groups = "keep") %>%
  unite(ids, scan_id, feature, na.rm = T, sep = " ") %>%
  column_to_rownames("ids") %>%
  pheatmap(., cluster_rows = F, cluster_cols = F)
```

# Comparison of scores between groups
